Methods for Large Scale Learning to Rank

### 2014-04-06 report/Chapters/CrossBenchmarkComparison.tex
verder werk aan 'proposed by'-referenties

AdaRank-\acs{nDCG} & \cite{Xu2007} & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} &  & \cite{Lin2010, Lin2011, Gao2014} \\ 
ADMM & \cite{Duh2011} & \cite{Duh2011} & ListNet &  &  \\ 

@@

Best Single Feature &  & \cite{Gomes2013} & MHR &  &  \\ 

@@

BT & \cite{Zhou2008} & \cite{Zhou2008} & PERF-\acs{MAP} &  & \cite{Torkestani2012b} \\ 

@@

CA & \cite{Metzler2007} & \cite{Busa-Fekete2013,Tan2013} & Q.D.\acs{KNN} &  & \cite{Wang2013} \\ 

@@

Consistent-RankCosine &  & \cite{Tan2013} & RankAgg\acs{nDCG} & \cite{Wang2013} & \cite{Wang2013} \\ 

@@

FocusedNet & \cite{Niu2012} & \cite{Niu2012} & RankNet &  & \cite{Busa-Fekete2013, Papini2012, Niu2012} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} &  & \cite{Busa-Fekete2013, Freno2011, He2010} \\ 
FRank &  & \cite{Wang2012} & Rank\acs{SVM}-Primal &  & \cite{Lai2011} \\ 

@@

FSM$^{\acs{SVM}}$ & & \cite{Lai2013c} & RCP & \cite{Elsas2008} & \cite{Elsas2008} \\ 
GAS-E &  & \cite{Lai2013c} & RE-QR & \cite{Veloso2010} & \cite{Veloso2010} \\ 

@@

Group\acs{CE} & \cite{Lin2011} & \cite{Lin2011} & RSRank &  & \cite{Lai2013} \\ 
Group\acs{MLE} & \cite{Lin2010} & \cite{Lin2011} & SmoothGrad &  & \cite{Tan2013} \\ 

@@

\acs{IP}Rank & \cite{Wang2009b} & \cite{Wang2009b, Torkestani2012} & SoftRank &  & \cite{Qin2010b} \\ 

@@

LambdaRank &  &  & TM & \cite{Zhou2008} & \cite{Zhou2008, Papini2012, Tan2013} \\ 

>>>>

AdaRank-\acs{nDCG} & \cite{Xu2007} & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} & \cite{Xia2008} & \cite{Lin2010, Lin2011, Gao2014} \\ 
ADMM & \cite{Duh2011} & \cite{Duh2011} & ListNet & \cite{Cao2007} &  \\ 

@@

Best Single Feature &  & \cite{Gomes2013} & MHR & \cite{Qin2007} &  \\ 

@@

BT & \cite{Zhou2008} & \cite{Zhou2008} & PERF-\acs{MAP} & \cite{Pan2011} & \cite{Torkestani2012b} \\ 

@@

CA & \cite{Metzler2007} & \cite{Busa-Fekete2013,Tan2013} & Q.D.\acs{KNN} & \cite{Geng2008} & \cite{Wang2013} \\ 

@@

Consistent-RankCosine & \cite{Ravikumar2011} & \cite{Tan2013} & RankAgg\acs{nDCG} & \cite{Wang2013} & \cite{Wang2013} \\ 

@@

FocusedNet & \cite{Niu2012} & \cite{Niu2012} & RankNet & \cite{Burges2005} & \cite{Busa-Fekete2013, Papini2012, Niu2012} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} & \cite{Herbrich1999, Joachims2002} & \cite{Busa-Fekete2013, Freno2011, He2010} \\ 
FRank & \cite{Tsai2007} & \cite{Wang2012} & Rank\acs{SVM}-Primal &  & \cite{Lai2011} \\ 

@@

FSM$^{\acs{SVM}}$ & \cite{Lai2013c} & \cite{Lai2013c} & RCP & \cite{Elsas2008} & \cite{Elsas2008} \\ 
GAS-E & \cite{Geng2007} & \cite{Lai2013c} & RE-QR & \cite{Veloso2010} & \cite{Veloso2010} \\ 

@@

Group\acs{CE} & \cite{Lin2011} & \cite{Lin2011} & RSRank & \cite{Sun2009} & \cite{Lai2013} \\ 
Group\acs{MLE} & \cite{Lin2010} & \cite{Lin2011} & SmoothGrad & \cite{Le2007} & \cite{Tan2013} \\ 

@@

\acs{IP}Rank & \cite{Wang2009b} & \cite{Wang2009b, Torkestani2012} & SoftRank & \cite{Taylor2008, Guiver2008} & \cite{Qin2010b} \\ 

@@

LambdaRank & \cite{Burges2006} &  & TM & \cite{Zhou2008} & \cite{Zhou2008, Papini2012, Tan2013} \\ 
